\section{Detailed use-case specifications}

\subsection{Use Case ``Register and Verify Account''}

\textbf{1. Use case code:} UC001

\textbf{2. Brief Description:} This use case describes the interaction between Customer and Bike Sharing System when the customer wishes to register, verify identity and access bike rental services. Because the bike is a valuable asset, the system must verify account ownership and customer identity before allowing rental.

\textbf{3. Actors}
\begin{itemize}
  \item Customer
\end{itemize}

\textbf{4. Included / related sub-use cases}
\begin{longtable}{P{0.18\textwidth}P{0.30\textwidth}P{0.42\textwidth}}
\toprule
\textbf{Sub UC} & \textbf{Name} & \textbf{Goal} \\
\midrule
UC001.1 & Register Customer Account & Customer creates an account with phone/email and password. \\
UC001.2 & Verify Contact Method & Customer proves ownership of phone/email by OTP. \\
UC001.3 & Submit Identity Verification & Customer submits identity data required before renting valuable assets. \\
UC001.4 & Log In Securely & Customer accesses an existing verified account. \\
UC001.5 & Recover Account Access & Customer resets password or recovers account using verified contact method. \\
Related & Review Customer Verification & Admin / Operator may manually review suspicious or failed identity requests; this is a separate operational use case, not the main UC001 actor flow. \\
\bottomrule
\end{longtable}

\textbf{5. Preconditions}
\begin{itemize}
  \item Customer has internet access and a reachable phone number or email.
  \item The system can send OTP messages through the configured provider.
  \item Identity verification policy and minimum rental eligibility rules are configured.
\end{itemize}

\textbf{6. Basic Flow of Events}
\begin{enumerate}
  \item Customer opens the application and chooses to register or log in.
  \item The software displays account access options and the verification requirement for bike rental.
  \item Customer enters account credentials and contact information (see Table A1).
  \item The software validates required fields, password strength and duplicate phone/email.
  \item The software sends an OTP to the selected contact method.
  \item Customer submits the OTP.
  \item The software verifies the OTP and creates or authenticates the account.
  \item Customer submits identity information and required identity evidence.
  \item The software validates the identity submission and determines identity status.
  \item The software displays access status, verification status and rental eligibility (see Table B1).
\end{enumerate}

\textbf{7. Alternative flows}
\begin{longtable}{P{0.06\textwidth}P{0.14\textwidth}P{0.25\textwidth}P{0.33\textwidth}P{0.12\textwidth}}
\caption{Alternative flows of events for UC001}\\
\toprule
\textbf{No} & \textbf{Location} & \textbf{Condition} & \textbf{Action} & \textbf{Resume} \\
\midrule
1 & Step 3 & Required account fields are missing or have invalid format. & The software rejects the submission, explains field-level errors and keeps the account uncreated. & Step 3 \\
2 & Step 4 & Phone number or email already belongs to another account. & The software blocks duplicate registration and offers login or account recovery. & Step 1 \\
3 & Step 4 & Password does not satisfy security policy. & The software displays password rules and asks Customer to submit a stronger password. & Step 3 \\
4 & Step 5 & OTP provider cannot deliver the code. & The software allows resend after cooldown and records OTP delivery failure for monitoring. & Step 5 \\
5 & Step 6 & OTP is incorrect, expired or submitted too many times. & The software rejects OTP; after the retry limit, it temporarily locks verification attempts. & Step 5 or Ends \\
6 & Step 7 & Login is from a new or risky device. & The software requires step-up OTP verification before allowing access. & Step 5 \\
7 & Step 8 & Identity evidence is unreadable or incomplete. & The software marks identity request as rejected and asks Customer to resubmit evidence. & Step 8 \\
8 & Step 9 & Identity data mismatches account data or blacklist/risk policy. & The software marks identity request as rejected or pending manual review and blocks rental. & Ends limited \\
9 & Step 9 & Verification requires manual review. & The software marks account as pending verification; Customer may use non-rental features but cannot rent bikes. & Ends pending \\
10 & Step 10 & Customer has unpaid debt or severe violation history. & The software allows login but marks rental eligibility as blocked until debt/violation is resolved. & Ends blocked \\
\bottomrule
\end{longtable}

\textbf{8. Input data}
\begin{longtable}{P{0.05\textwidth}P{0.18\textwidth}P{0.26\textwidth}P{0.11\textwidth}P{0.24\textwidth}P{0.08\textwidth}}
\caption{Table A1 - Input data of account registration and verification}\\
\toprule
\textbf{No} & \textbf{Data fields} & \textbf{Description} & \textbf{Mandatory} & \textbf{Valid condition} & \textbf{Example} \\
\midrule
1 & FullName & Customer legal or registered name. & Yes & 2--100 characters. & Nguyen Van A \\
2 & PhoneNumber & Primary phone number for account and OTP. & Yes & Valid, unique, reachable. & 0912345678 \\
3 & Email & Optional email for receipt and recovery. & No & Valid format if provided. & user@gmail.com \\
4 & Password & Secret credential for login. & Yes & Meets password policy. & Abc12345! \\
5 & OTP & Verification code sent by system. & Yes & Correct, unexpired, within retry limit. & 123456 \\
6 & IdentityNumber & Citizen ID, passport, student ID or equivalent. & Yes before rental & Valid format and not blacklisted. & 001203000001 \\
7 & IdentityEvidence & Identity document/selfie evidence reference. & Yes before rental & Clear image, accepted type, not reused suspiciously. & id-front.jpg \\
\bottomrule
\end{longtable}

\textbf{9. Output data}
\begin{longtable}{P{0.05\textwidth}P{0.20\textwidth}P{0.35\textwidth}P{0.17\textwidth}P{0.13\textwidth}}
\caption{Table B1 - Output data of account registration and verification}\\
\toprule
\textbf{No} & \textbf{Data fields} & \textbf{Description} & \textbf{Display format} & \textbf{Example} \\
\midrule
1 & UserID & Unique ID of the customer account. & String & U001 \\
2 & AccessStatus & Login or registration result. & String & Authenticated \\
3 & IdentityStatus & Verification result. & String & Verified \\
4 & RentalEligibility & Whether Customer can start rental. & Text/Boolean & Eligible \\
5 & BlockReason & Reason if rental is blocked. & Text & Unpaid debt \\
\bottomrule
\end{longtable}

\textbf{10. Acceptance rules}
\begin{itemize}
  \item A customer cannot start UC003 unless IdentityStatus is \textit{Verified}.
  \item OTP must expire and must have a retry limit.
  \item Duplicate phone numbers are not accepted for active customer accounts.
  \item A locked/suspended account may log in only if policy allows, but cannot rent bikes.
\end{itemize}

\newpage
\subsection{Use Case ``Manage Wallet and Rental Packages''}

\textbf{1. Use case code:} UC002

\textbf{2. Brief Description:} This use case describes the interaction between Customer, Payment Gateway and Bike Sharing System when the customer wishes to top up the prepaid wallet, buy a day/month package, or review payment/package status before renting.

\textbf{3. Actors}
\begin{itemize}
  \item Customer
  \item Payment Gateway
\end{itemize}

\textbf{4. Included / related sub-use cases}
\begin{longtable}{P{0.18\textwidth}P{0.30\textwidth}P{0.42\textwidth}}
\toprule
\textbf{Sub UC} & \textbf{Name} & \textbf{Goal} \\
\midrule
UC002.1 & Top Up Wallet & Customer adds prepaid balance to wallet. \\
UC002.2 & Buy Day Pass & Customer buys a short-term rental package. \\
UC002.3 & Buy Monthly Pass & Customer buys a longer-term package for repeated usage. \\
UC002.4 & View Wallet and Package History & Customer reviews balance, package validity and transaction history. \\
UC002.5 & Retry or Cancel Pending Payment & Customer handles a payment that has no final result yet. \\
\bottomrule
\end{longtable}

\textbf{5. Preconditions}
\begin{itemize}
  \item Customer is logged in with an active account.
  \item Customer wallet exists and is not locked.
  \item Payment Gateway is available or pending payment policy is configured.
  \item Active package catalog, prices and validity rules are configured.
\end{itemize}

\textbf{6. Basic Flow of Events}
\begin{enumerate}
  \item Customer opens Wallet and Packages.
  \item The software displays wallet balance, held amount, active packages and available packages.
  \item Customer selects Top Up Wallet, Buy Day Pass, Buy Monthly Pass or View History.
  \item For payment actions, Customer enters amount or selects package and payment method (see Table A2).
  \item The software validates wallet status, amount limits, package availability and customer status.
  \item The software creates a pending wallet transaction.
  \item The software sends payment request to Payment Gateway.
  \item Payment Gateway returns payment result.
  \item The software updates wallet balance or activates the package.
  \item The software displays transaction receipt, updated wallet and package status (see Table B2).
\end{enumerate}

\textbf{7. Alternative flows}
\begin{longtable}{P{0.06\textwidth}P{0.14\textwidth}P{0.25\textwidth}P{0.33\textwidth}P{0.12\textwidth}}
\caption{Alternative flows of events for UC002}\\
\toprule
\textbf{No} & \textbf{Location} & \textbf{Condition} & \textbf{Action} & \textbf{Resume} \\
\midrule
1 & Step 2 & Wallet is locked due to fraud, debt or admin action. & The software displays lock reason and blocks new top-up/package purchase if policy requires. & Ends \\
2 & Step 4 & Top-up amount is outside allowed limits. & The software rejects the amount and shows minimum/maximum rules. & Step 4 \\
3 & Step 4 & Selected package is expired, hidden or inactive. & The software refreshes package catalog and asks Customer to choose another package. & Step 3 \\
4 & Step 5 & Customer is unverified. & The software allows balance top-up but marks rental/package usage as blocked until verification is completed. & Ends limited \\
5 & Step 7 & Payment Gateway times out before final result. & The software keeps transaction pending and prevents duplicate credit until reconciliation completes. & Step 10 pending \\
6 & Step 8 & Payment is declined. & The software marks transaction failed and allows retry with another method. & Step 4 \\
7 & Step 8 & Gateway returns success but callback is duplicated. & The software ignores duplicate callback using gateway transaction ID and does not credit twice. & Step 10 \\
8 & Step 9 & Customer already has an active package of same type. & The software applies configured rule: extend validity, queue next package or reject purchase. & Step 10 \\
9 & Step 9 & Wallet update fails after successful payment. & The software marks transaction for reconciliation and does not show balance until fixed. & Ends pending \\
10 & Step 10 & Customer requests transaction history. & The software displays filtered wallet/package history without starting a payment. & Ends \\
\bottomrule
\end{longtable}

\textbf{8. Input data}
\begin{longtable}{P{0.05\textwidth}P{0.18\textwidth}P{0.26\textwidth}P{0.11\textwidth}P{0.24\textwidth}P{0.08\textwidth}}
\caption{Table A2 - Input data of wallet and packages}\\
\toprule
\textbf{No} & \textbf{Data fields} & \textbf{Description} & \textbf{Mandatory} & \textbf{Valid condition} & \textbf{Example} \\
\midrule
1 & CustomerID & Customer who performs transaction. & Yes & Existing active customer. & U001 \\
2 & TransactionType & Wallet/package action. & Yes & TopUp, BuyDayPass, BuyMonthlyPass, ViewHistory. & TopUp \\
3 & Amount & Money paid by Customer. & Yes for payment & Positive amount within policy. & 100000 \\
4 & PackageID & Package selected by Customer. & Yes for package & Existing active package. & MONTHLY01 \\
5 & PaymentMethod & Gateway payment method. & Yes for payment & Supported method. & BankCard \\
6 & IdempotencyKey & Unique client transaction key. & Yes & Unique for request retry. & TX-abc-01 \\
\bottomrule
\end{longtable}

\textbf{9. Output data}
\begin{longtable}{P{0.05\textwidth}P{0.20\textwidth}P{0.35\textwidth}P{0.17\textwidth}P{0.13\textwidth}}
\caption{Table B2 - Output data of wallet and packages}\\
\toprule
\textbf{No} & \textbf{Data fields} & \textbf{Description} & \textbf{Display format} & \textbf{Example} \\
\midrule
1 & TransactionID & Unique wallet transaction. & String & WT9001 \\
2 & WalletBalance & Available wallet balance. & Currency & 85000 VND \\
3 & HoldAmount & Balance temporarily reserved for active ride. & Currency & 20000 VND \\
4 & PackageStatus & Current package status. & String & Active \\
5 & PaymentStatus & Gateway/payment status. & String & Paid \\
6 & ValidUntil & Package expiry time if applicable. & Datetime & 2026-06-12 \\
\bottomrule
\end{longtable}

\textbf{10. Acceptance rules}
\begin{itemize}
  \item Successful payment must create exactly one successful wallet transaction.
  \item Package validity and remaining minutes must be visible before Customer starts a ride.
  \item Pending payment must not increase wallet balance until confirmed.
  \item Penalty debt cannot be hidden by buying a package.
\end{itemize}

\newpage
\subsection{Use Case ``Rent Bike by Hour''}

\textbf{1. Use case code:} UC003

\textbf{2. Brief Description:} This use case describes the interaction between Customer, GPS / Map Service and Bike Sharing System when the customer wishes to find an available bike, satisfy rental eligibility rules and start an hourly ride.

\textbf{3. Actors}
\begin{itemize}
  \item Customer
  \item GPS / Map Service
\end{itemize}

\textbf{4. Included / related sub-use cases}
\begin{longtable}{P{0.18\textwidth}P{0.30\textwidth}P{0.42\textwidth}}
\toprule
\textbf{Sub UC} & \textbf{Name} & \textbf{Goal} \\
\midrule
UC003.1 & Search Available Bikes & Customer finds rentable bikes or stations nearby. \\
UC003.2 & Scan Bike QR Code & Customer identifies a specific bike to rent. \\
UC003.3 & Start Hourly Ride & Customer starts a ride after eligibility and bike checks pass. \\
UC003.4 & Apply Active Package & Customer uses a valid day/month package for the ride if applicable. \\
UC003.5 & View Active Ride & Customer monitors active ride time, bike and charging rule. \\
\bottomrule
\end{longtable}

\textbf{5. Preconditions}
\begin{itemize}
  \item Customer is logged in, verified and not suspended.
  \item Customer has no active ride and no blocking unpaid penalty.
  \item Customer has sufficient wallet balance/hold amount or an active package.
  \item Bike, station and lock status are synchronized enough to make a rental decision.
\end{itemize}

\textbf{6. Basic Flow of Events}
\begin{enumerate}
  \item Customer opens map, nearby bikes or scan screen.
  \item The software requests current location from GPS / Map Service.
  \item GPS / Map Service returns location or selected search area.
  \item The software displays available bikes/stations and important rental rules.
  \item Customer selects a bike or scans the bike QR code (see Table A3).
  \item The software verifies account, wallet/package, active ride, debt, bike status and lock status.
  \item The software displays hourly price, package coverage, wallet hold and penalty rules.
  \item Customer accepts rental conditions.
  \item The software creates ride record and reserves required wallet hold or package usage.
  \item The software sends unlock command and receives successful lock response.
  \item The software marks ride as in progress and bike as in use.
  \item The software displays active ride details (see Table B3).
\end{enumerate}

\textbf{7. Alternative flows}
\begin{longtable}{P{0.06\textwidth}P{0.14\textwidth}P{0.25\textwidth}P{0.33\textwidth}P{0.12\textwidth}}
\caption{Alternative flows of events for UC003}\\
\toprule
\textbf{No} & \textbf{Location} & \textbf{Condition} & \textbf{Action} & \textbf{Resume} \\
\midrule
1 & Step 2 & Customer denies location permission. & The software allows manual station search or QR scan without current location. & Step 4 \\
2 & Step 4 & No available bike is found nearby. & The software suggests larger radius, another station or later retry. & Step 4 \\
3 & Step 5 & QR code is invalid, damaged or belongs to another system. & The software rejects the scan and asks Customer to scan another bike. & Step 5 \\
4 & Step 6 & Account is not verified, suspended or has unpaid debt. & The software blocks rental and shows the exact reason and required recovery action. & Ends \\
5 & Step 6 & Customer already has an active ride. & The software opens the active ride screen instead of creating another ride. & Ends \\
6 & Step 6 & Wallet balance is below required hold and no active package is available. & The software redirects Customer to top up wallet or buy a package. & UC002 \\
7 & Step 6 & Bike becomes unavailable after map display. & The software rejects rental and refreshes availability. & Step 4 \\
8 & Step 6 & Bike is under maintenance or lock status is offline. & The software blocks rental, hides the bike from available list and may create inspection signal. & Step 4 \\
9 & Step 8 & Customer refuses rental rules or price. & The software cancels rental attempt without wallet hold. & Ends \\
10 & Step 9 & Ride record is created but wallet hold fails. & The software cancels pending ride and keeps bike available. & Ends \\
11 & Step 10 & Unlock command fails or times out. & The software retries according to policy, then cancels ride, releases hold and marks bike for inspection. & Ends \\
12 & Step 12 & App loses network after unlock succeeds. & The software keeps ride in progress on server and shows active ride when Customer reconnects. & Ends active \\
\bottomrule
\end{longtable}

\textbf{8. Input data}
\begin{longtable}{P{0.05\textwidth}P{0.18\textwidth}P{0.26\textwidth}P{0.11\textwidth}P{0.24\textwidth}P{0.08\textwidth}}
\caption{Table A3 - Input data of hourly bike rental}\\
\toprule
\textbf{No} & \textbf{Data fields} & \textbf{Description} & \textbf{Mandatory} & \textbf{Valid condition} & \textbf{Example} \\
\midrule
1 & CustomerID & Customer who starts rental. & Yes & Verified active customer. & U001 \\
2 & CurrentLocation & Customer location. & No & Valid latitude/longitude if provided. & 21.005,105.843 \\
3 & BikeID & Selected/scanned bike. & Yes & Existing available bike. & B102 \\
4 & StationID & Current station/area of the bike. & Yes & Active station/allowed area. & S01 \\
5 & RentalMode & Charging mode. & Yes & Hourly, DayPass, MonthlyPass. & Hourly \\
6 & AcceptedRuleVersion & Rental rules accepted by Customer. & Yes & Current active version. & RULE2026A \\
\bottomrule
\end{longtable}

\textbf{9. Output data}
\begin{longtable}{P{0.05\textwidth}P{0.20\textwidth}P{0.35\textwidth}P{0.17\textwidth}P{0.13\textwidth}}
\caption{Table B3 - Output data of hourly bike rental}\\
\toprule
\textbf{No} & \textbf{Data fields} & \textbf{Description} & \textbf{Display format} & \textbf{Example} \\
\midrule
1 & RideID & Unique active ride ID. & String & R5001 \\
2 & RideStatus & Current ride status. & String & In progress \\
3 & BikeStatus & Current bike status. & String & In use \\
4 & StartedAt & Rental start time. & Datetime & 2026-05-12 08:30 \\
5 & WalletHold & Reserved wallet balance. & Currency & 20000 VND \\
6 & AppliedPackage & Package applied if any. & String & MONTHLY01 \\
7 & ActiveRuleVersion & Rule version applied to ride. & String & RULE2026A \\
\bottomrule
\end{longtable}

\textbf{10. Acceptance rules}
\begin{itemize}
  \item The system must not create two active rides for one customer.
  \item Bike status must change from \textit{available} to \textit{in\_use} only after successful ride start.
  \item Wallet hold/package reservation must be released if unlock fails.
  \item Customer must see the applicable price/package/penalty rules before confirmation.
\end{itemize}

\newpage
\subsection{Use Case ``End Ride and Settle Charges''}

\textbf{1. Use case code:} UC004

\textbf{2. Brief Description:} This use case describes the interaction between Customer and Bike Sharing System when the customer wishes to end a ride. The system checks return rules, calculates hourly fee, package coverage, overtime and penalties, then deducts the final amount from the prepaid wallet.

\textbf{3. Actors}
\begin{itemize}
  \item Customer
\end{itemize}

\textbf{4. Included / related sub-use cases}
\begin{longtable}{P{0.18\textwidth}P{0.30\textwidth}P{0.42\textwidth}}
\toprule
\textbf{Sub UC} & \textbf{Name} & \textbf{Goal} \\
\midrule
UC004.1 & Return Bike & Customer returns bike to valid station/area. \\
UC004.2 & Lock and End Ride & Customer locks bike and requests ride completion. \\
UC004.3 & Report Bike Issue & Customer reports damage or safety issue discovered during/after ride. \\
UC004.4 & Settle Ride Charge & Customer pays ride fee, overtime fee and penalties from wallet. \\
UC004.5 & View Receipt & Customer receives receipt and wallet/package update. \\
UC004.6 & Pay Outstanding Balance & Customer clears debt if wallet is insufficient. \\
UC004.7 & Dispute Penalty & Customer asks Admin / Operator to review a penalty; this is related but can be handled after settlement. \\
\bottomrule
\end{longtable}

\textbf{5. Preconditions}
\begin{itemize}
  \item Customer has an active ride.
  \item Bike can be locked or lock status can be verified.
  \item Settlement rules, package usage and penalty rules are available.
\end{itemize}

\textbf{6. Basic Flow of Events}
\begin{enumerate}
  \item Customer reaches a station or allowed return area.
  \item Customer locks the bike and selects End Ride.
  \item The software asks Customer to confirm return location, lock status and optional bike condition note (see Table A4).
  \item The software verifies return area, lock status and ride duration.
  \item The software calculates base hourly fee and package-covered minutes.
  \item The software checks violation rules: wrong return, unlocked bike, overtime, damage/loss report or debt rule.
  \item The software creates penalty records for detected violations.
  \item The software calculates final charge and deducts wallet balance/hold.
  \item The software updates ride, bike, wallet, package and issue report status.
  \item The software displays receipt, updated wallet balance and penalty/issue report result (see Table B4).
\end{enumerate}

\textbf{7. Alternative flows}
\begin{longtable}{P{0.06\textwidth}P{0.14\textwidth}P{0.25\textwidth}P{0.33\textwidth}P{0.12\textwidth}}
\caption{Alternative flows of events for UC004}\\
\toprule
\textbf{No} & \textbf{Location} & \textbf{Condition} & \textbf{Action} & \textbf{Resume} \\
\midrule
1 & Step 1 & Customer is outside valid return area. & The software warns Customer and shows nearest valid station/area; if Customer confirms wrong return, penalty rule is applied. & Step 3 or Step 6 \\
2 & Step 2 & Bike is not locked. & The software refuses normal completion and asks Customer to lock bike; ride time continues until lock is confirmed. & Step 2 \\
3 & Step 4 & Lock signal cannot be synchronized. & The software creates pending review, stores Customer evidence and may keep ride pending until Admin review. & Ends pending \\
4 & Step 5 & Active package covers entire ride. & The software sets base ride fee to zero but still checks overtime/penalty rules. & Step 6 \\
5 & Step 5 & Ride exceeds package included minutes. & The software calculates overtime fee from package overtime rate or hourly policy. & Step 6 \\
6 & Step 6 & Wrong return area, unlocked return, damage, loss or overdue debt is detected. & The software creates one or more penalties using PENALTY\_RULES. & Step 7 \\
7 & Step 8 & Wallet balance is insufficient. & The software deducts available amount, records outstanding balance and blocks new rentals until paid. & Step 9 \\
8 & Step 8 & Wallet deduction fails due to concurrency or ledger error. & The software marks settlement pending and prevents duplicate deduction until reconciliation. & Ends pending \\
9 & Step 9 & Customer reports a bike issue. & The software creates ISSUE\_REPORTS and marks bike as inspection required if issue affects safety. & Step 10 \\
10 & Step 9 & Bike is returned normally with no issue. & The software marks bike available for next rental. & Step 10 \\
11 & Step 10 & Customer disputes a penalty. & The software records a dispute request while keeping charge according to policy until review completes. & Ends \\
12 & Step 10 & Receipt generation fails. & The software completes settlement and lets Customer view receipt later from ride history. & Ends \\
\bottomrule
\end{longtable}

\textbf{8. Input data}
\begin{longtable}{P{0.05\textwidth}P{0.18\textwidth}P{0.26\textwidth}P{0.11\textwidth}P{0.24\textwidth}P{0.08\textwidth}}
\caption{Table A4 - Input data of ride settlement}\\
\toprule
\textbf{No} & \textbf{Data fields} & \textbf{Description} & \textbf{Mandatory} & \textbf{Valid condition} & \textbf{Example} \\
\midrule
1 & RideID & Active ride to be completed. & Yes & Existing in-progress ride. & R5001 \\
2 & EndStationID & Return station/area. & Yes & Valid active station/area or flagged wrong return. & S03 \\
3 & LockConfirmation & Lock signal or customer confirmation. & Yes & True or pending-review evidence. & True \\
4 & EndedAt & Ride end request time. & Yes & After StartedAt. & 2026-05-12 09:05 \\
5 & BikeConditionNote & Optional issue note. & No & Text up to configured limit. & Brake issue \\
6 & EvidenceImage & Optional photo for issue/dispute. & No & Accepted image type. & issue.jpg \\
7 & RuleVersion & Rule version used at settlement. & Yes & Active at ride start/end per policy. & RULE2026A \\
\bottomrule
\end{longtable}

\textbf{9. Output data}
\begin{longtable}{P{0.05\textwidth}P{0.20\textwidth}P{0.35\textwidth}P{0.17\textwidth}P{0.13\textwidth}}
\caption{Table B4 - Output data of ride settlement}\\
\toprule
\textbf{No} & \textbf{Data fields} & \textbf{Description} & \textbf{Display format} & \textbf{Example} \\
\midrule
1 & ReceiptID & Settlement receipt ID. & String & RC9001 \\
2 & RideStatus & Final ride status. & String & Completed \\
3 & RideFee & Fee after package coverage. & Currency & 12000 VND \\
4 & PenaltyAmount & Total penalty amount. & Currency & 50000 VND \\
5 & TotalCharge & Final deducted amount. & Currency & 62000 VND \\
6 & WalletBalance & Balance after settlement. & Currency & 38000 VND \\
7 & IssueReportID & Issue report if created. & String & IR3001 \\
\bottomrule
\end{longtable}

\textbf{10. Acceptance rules}
\begin{itemize}
  \item A completed ride must have exactly one settlement result or a clear pending-review status.
  \item Package may reduce ride fee but must not remove penalty charges.
  \item Wallet deduction must be auditable in WALLET\_TRANSACTIONS.
  \item Unsafe bikes must not become available after settlement.
\end{itemize}

\newpage
\subsection{Use Case ``Resolve Bike Maintenance Request''}

\textbf{1. Use case code:} UC005

\textbf{2. Brief Description:} This use case describes the interaction between Admin / Operator, Maintenance Staff and Bike Sharing System when a reported or detected bike issue must be reviewed, assigned, repaired and closed. Customer is not an actor of this use case; Customer only creates an issue report that can trigger this workflow.

\textbf{3. Actors}
\begin{itemize}
  \item Admin / Operator
  \item Maintenance Staff
\end{itemize}

\textbf{4. Included / related sub-use cases}
\begin{longtable}{P{0.18\textwidth}P{0.30\textwidth}P{0.42\textwidth}}
\toprule
\textbf{Sub UC} & \textbf{Name} & \textbf{Goal} \\
\midrule
UC005.1 & Review Issue Report & Admin / Operator evaluates report validity and severity. \\
UC005.2 & Create or Merge Maintenance Request & Admin / Operator creates a request or merges duplicated reports. \\
UC005.3 & Assign Maintenance Task & Admin / Operator assigns repair work to available staff. \\
UC005.4 & Update Repair Result & Maintenance Staff records inspection and repair result. \\
UC005.5 & Release or Retire Bike & Admin / Operator or Maintenance Staff marks bike available, still unsafe or retired. \\
\bottomrule
\end{longtable}

\textbf{5. Preconditions}
\begin{itemize}
  \item A bike exists in the system.
  \item An issue report, failed lock event or operational inspection indicates that the bike may need maintenance.
  \item Admin / Operator and Maintenance Staff are authenticated with appropriate roles.
\end{itemize}

\textbf{6. Basic Flow of Events}
\begin{enumerate}
  \item Admin / Operator opens issue reports or bikes requiring inspection.
  \item Admin / Operator reviews report details, ride link, evidence and bike status (see Table A5).
  \item The software creates a maintenance request or links the report to an existing open request.
  \item The software marks the bike as maintenance or inspection required.
  \item Admin / Operator sets priority and assigns the request to Maintenance Staff.
  \item Maintenance Staff receives the assigned maintenance task.
  \item Maintenance Staff inspects the bike, performs repair or records that repair cannot be completed.
  \item Maintenance Staff updates repair notes, parts used, final safety status and evidence.
  \item The software validates required closure data and updates request status.
  \item The software updates bike status and related issue reports (see Table B5).
\end{enumerate}

\textbf{7. Alternative flows}
\begin{longtable}{P{0.06\textwidth}P{0.14\textwidth}P{0.25\textwidth}P{0.33\textwidth}P{0.12\textwidth}}
\caption{Alternative flows of events for UC005}\\
\toprule
\textbf{No} & \textbf{Location} & \textbf{Condition} & \textbf{Action} & \textbf{Resume} \\
\midrule
1 & Step 2 & Issue report is invalid, spam or unrelated to the bike. & Admin / Operator rejects report with reason and keeps bike status unchanged if no safety risk exists. & Ends \\
2 & Step 3 & The bike already has an open maintenance request. & The software merges the report into existing request and updates priority if needed. & Step 5 \\
3 & Step 4 & Issue indicates severe safety risk. & The software immediately hides bike from rental and marks it unavailable before assignment. & Step 5 \\
4 & Step 5 & No Maintenance Staff is available. & The software keeps request unassigned, notifies Admin / Operator and maintains bike as unavailable. & Step 5 \\
5 & Step 5 & Assigned staff rejects task due to area/skill mismatch. & Admin / Operator reassigns task or changes priority/area. & Step 5 \\
6 & Step 7 & Bike cannot be found at expected station. & Maintenance Staff marks request as bike missing; Admin / Operator starts lost-bike handling. & Ends escalated \\
7 & Step 7 & Repair requires parts or external service. & Maintenance Staff marks request waiting for parts/external repair and records expected follow-up. & Step 7 \\
8 & Step 8 & Closure data is incomplete. & The software blocks closure and asks staff to add final status, repair note and evidence. & Step 8 \\
9 & Step 9 & Bike fails safety check after repair. & The software keeps bike in maintenance status and escalates to Admin / Operator. & Ends unresolved \\
10 & Step 10 & Bike is repaired and passes safety check. & The software marks request closed and bike available at its current station. & Ends \\
\bottomrule
\end{longtable}

\textbf{8. Input data}
\begin{longtable}{P{0.05\textwidth}P{0.18\textwidth}P{0.26\textwidth}P{0.11\textwidth}P{0.24\textwidth}P{0.08\textwidth}}
\caption{Table A5 - Input data of maintenance request}\\
\toprule
\textbf{No} & \textbf{Data fields} & \textbf{Description} & \textbf{Mandatory} & \textbf{Valid condition} & \textbf{Example} \\
\midrule
1 & ReportID & Issue report that triggered maintenance. & No & Existing open report if available. & IR3001 \\
2 & BikeID & Bike affected by the issue. & Yes & Existing bike. & B102 \\
3 & Priority & Operational severity. & Yes & Low, Medium, High, Critical. & High \\
4 & IssueDescription & Problem reviewed by Admin / Operator. & Yes & Meaningful text. & Brake loose \\
5 & AssignedStaffID & Staff member assigned to repair. & Yes when assigned & Existing active staff. & ST05 \\
6 & RepairNote & Inspection and repair result. & Yes when closing & Meaningful text. & Adjusted brake \\
7 & FinalBikeStatus & Status after maintenance. & Yes when closing & Available, Maintenance, Retired, Lost. & Available \\
\bottomrule
\end{longtable}

\textbf{9. Output data}
\begin{longtable}{P{0.05\textwidth}P{0.20\textwidth}P{0.35\textwidth}P{0.17\textwidth}P{0.13\textwidth}}
\caption{Table B5 - Output data of maintenance request}\\
\toprule
\textbf{No} & \textbf{Data fields} & \textbf{Description} & \textbf{Display format} & \textbf{Example} \\
\midrule
1 & RequestID & Maintenance request ID. & String & M3001 \\
2 & RequestStatus & Current/final request status. & String & Closed \\
3 & BikeStatus & Updated bike status. & String & Available \\
4 & AssignedStaff & Staff assigned to request. & Text & Nguyen Van B \\
5 & ResolvedAt & Completion time. & Datetime & 2026-05-12 15:20 \\
6 & LinkedReports & Issue reports resolved/merged by this request. & List & IR3001, IR3002 \\
\bottomrule
\end{longtable}

\textbf{10. Acceptance rules}
\begin{itemize}
  \item Customer is not connected to UC005 in the use-case diagram.
  \item A bike with an open safety-related maintenance request must not be rentable.
  \item Request closure requires final bike status and repair note.
  \item Duplicated issue reports should be merged rather than creating many open requests for one bike.
\end{itemize}
